---
title: "Supplementary material"
# author: 
#       - name: Diego Mendicino
#       - name: Tamara Ricardo
#       - name: Maximiliano Cristaldi
#       - name: Mariana Maglianese
#       - name: Gastón Guzmán
#       - name: Sebastián Claussen
#       - name: Romina Chiaraviglio
#       - name: Federico Costa
#       - name: Christian Ávalos
#       - name: Andrea Previtali
    
format: 
  pdf:
    papersize: a4
    mainfont: "Palatino Linotype"
    fontsize: 10pt
    geometry:
      - top=25mm
      - left=25mm
      - heightrounded
---


```{r}
#| echo: false
#| id: setup
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.asp = 1.25
)
```

```{r}
#| id: Load packages
pacman::p_load(
  gtsummary,
  flextable,
  epiR,
  epikit,
  rio,
  janitor,
  tidyverse
)
```

```{r}
#| id: Load data
data <- import("clean/kap_dengue.rds")
```

```{r}
#| id: gtsummary format
gt_format <- function(x) {
  x |>

    add_p(pvalue_fun = label_style_pvalue(digits = 3)) |>

    # Table layout
    bold_labels() |>
    bold_p() |>
    modify_indent(columns = label, indent = 0) |>
    remove_footnote_header(columns = all_stat_cols()) |>
    as_flex_table() |>
    font(fontname = "Palatino Linotype", part = "all") |>
    fontsize(size = 10, part = "all") |>
    width(width = c(4, 2.5, 2.5, 2.5, 2.5, 1.5), unit = "cm")
}
```

<!-- ## Supplementary material -->

### Table S1. Demographic data of the study participants, Santa Fe, Argentina (2019-2020).

```{r}
#| id: tabs1
tabs1 <- data |>
  tbl_summary(
    by = barrio,
    include = c(genero, educacion, ocupacion),
    digits = list(all_categorical() ~ c(0, 1)),
    missing = "no"
  ) |>
  add_overall()

# Show table
tabs1 |>
  gt_format()
```

\newpage

### Table S2. Knowledge about dengue by neighborhood, Santa Fe, Argentina (2019-2020).

```{r}
#| id: tabs2
tabs2 <- data |>
  tbl_summary(
    by = barrio,
    include = c(
      conoce_dengue:con_alguien_hogar,
      dengue_previo,
      con_sint_fiebre:con_sint_dol_ojos,
      con_sint_ns,
      con_trasm_mosquito:con_trasm_viaje,
      con_trasm_ns
    ),
    digits = list(all_categorical() ~ c(0, 1)),
    missing = "no"
  ) |>
  add_overall() |>

  # Agrupar variables síntomas
  add_variable_group_header(
    header = "Dengue symptoms",
    variables = con_sint_fiebre:con_sint_ns
  ) |>

  # Agrupar variables transmisión
  add_variable_group_header(
    header = "Ways of transmission",
    variables = con_trasm_mosquito:con_trasm_ns
  )

# Show table
tabs2 |>
  gt_format()
```

\newpage

### Table S3: Perceptions of the risk of dengue compared to leptospirosis among participants, Santa Fe, Argentina (2019-2020). 

```{r}
#| id: tabs3
tabs3 <- data |>
  # Generar tabla
  tbl_summary(
    by = barrio,
    include = c(
      act_mas_miedo:act_sint6m_acciones,
      act_problemas_barrio_cat:act_mejoras_barrio
    ),
    missing = "no",
    digits = list(all_categorical() ~ c(0, 1))
  ) |>

  # Añadir significancia
  add_overall() |>

  # Agrupar variables síntomas febrilews
  add_variable_group_header(
    header = "Febrile illness symptoms (6 months)",
    variables = act_sint6m_alguno:act_sint6m_acciones
  )

# Show table
tabs3 |>
  gt_format()
```

\newpage

### Table S4: Preventive practices against dengue among the study participants, Santa Fe, Argentina (2019-2020). 

```{r}
#| id: tabs4
tabs4 <- data |>
  tbl_summary(
    by = barrio,
    include = starts_with("prac") & !matches("prac_cacharros"),
    missing = "no",
    digits = list(all_categorical() ~ c(0, 1))
  ) |>

  # Añadir significancia
  add_overall() |>

  # Agrupar variables síntomas
  add_variable_group_header(
    header = "Avoids storage of environmental water",
    variables = prac_no_cacharros:prac_no_agua_lluvia
  ) |>

  # Agrupar variables transmisión
  add_variable_group_header(
    header = "Garbage disposal",
    variables = prac_resid_camion:prac_resid_no_rio
  )

# Show table
tabs4 |>
  gt_format()
```

\newpage

### Table S5: KAPs scores by neighborhood, Santa Fe, Argentina (2019-2020). 

```{r}
#| id: tabs5
tabs5 <- data |>
  tbl_summary(
    by = barrio,
    include = starts_with("sc_"),
    type = list(starts_with("sc_") ~ "continuous")
  ) |>

  # Añadir significancia
  add_overall()

# Show table
tabs5 |>
  gt_format()
```

\newpage

### Figure S6: Kendall’s correlation among KAPs scores, Santa Fe, Argentina (2019-2020).

```{r}
#| id: figs6
data |>
  select(
    "Knowledge" = sc_conocimientos,
    "Attitudes" = sc_actitudes,
    "Practices" = sc_practicas
  ) |>

  GGally::ggcorr(
    method = c("pairwise", "kendall"),
    label = TRUE,
    label_round = 3
  ) +

  scico::scale_fill_scico(palette = "managua", direction = -1, begin = .75)
```

\newpage

### Table S7: ELISA positivity and DENV seroprevalence by neighborhood, Santa Fe, Argentina (2019-2020). 

```{r}
#| id: tabs7
# Raw frequencies
tabs7 <- data |>
  tabyl(barrio, ELISA_dengue) |>
  adorn_totals(where = c("row", "col")) |>
  (\(x) {
    epi.prev(
      pos = x$POS,
      tested = x$Total,
      se = 0.96,
      sp = 0.93,
      units = 1
    ) |>
      list_rbind(names_to = "name")
  })() |>

  mutate(Site = rep(c("CH", "CS", "VP", "Total"), 8)) |>

  unite_ci("value", est, lower, upper, m100 = FALSE) |>
  pivot_wider(names_from = name, values_from = value)


# Show table
tabs7 |>
  select(
    Site,
    "Positives Test" = test.positive,
    "Positives True" = true.positive,
    "Positives False" = false.positive,
    "Seroprevalence Apparent" = ap,
    "Seroprevalence True" = tp
  ) |>

  flextable() |>
  font(fontname = "Palatino Linotype", part = "all") |>
  fontsize(size = 10, part = "all") |>
  separate_header(split = " ", opts = "span-top") |>
  width(width = rep(2.5, 6), unit = "cm")
```