---
title: "Unrecognized dengue transmission in socially vulnerable periurban neighborhoods of a temperate Argentine city: integrating serology with knowledge, attitudes and practices"
author: 
      - name: Diego Mendicino
      - name: Tamara Ricardo
      - name: Maximiliano Cristaldi
      - name: Mariana Maglianese
      - name: Gastón Guzmán
      - name: Sebastián Claussen
      - name: Romina Chiaraviglio
      - name: Federico Costa
      - name: Christian Ávalos
      - name: Andrea Previtali
    
format: html
---


```{r}
#| echo: false
#| id: setup
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.asp = 1.25
)
```

```{r}
#| id: load analysis
source("script_analysis_denv.R")
```

```{r}
#| id: gtsummary format
gt_format <- function(x) {
  x |>
    add_overall() |>
    add_p(pvalue_fun = label_style_pvalue(digits = 3)) |>

    # Table layout
    bold_labels() |>
    bold_p() |>
    modify_indent(columns = label, indent = 0) |>
    as_flex_table()
}
```

## Supplementary material

### Table S1. Demographic data of the study participants, Santa Fe, Argentina (2019-2020).

```{r}
#| id: tabs1
tabs1 |>
  gt_format()
```

\newpage

### Table S2. Knowledge about dengue by neighborhood, Santa Fe, Argentina (2019-2020).

```{r}
#| id: tabs2
tabs2 |>
  gt_format()
```

### Table S3: Perceptions of the risk of dengue compared to leptospirosis among participants, Santa Fe, Argentina (2019-2020). 

### Table S4: Preventive practices against dengue among the study participants, Santa Fe, Argentina (2019-2020). 

### Table S5: KAPs scores by neighborhood, Santa Fe, Argentina (2019-2020). 

### Figure S6: Kendall’s correlation among KAPs scores, Santa Fe, Argentina (2019-2020).

### Table S7: ELISA positivity and DENV seroprevalence by neighborhood, Santa Fe, Argentina (2019-2020). 